Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Spacing fix for (cons a_i d_i)

\begin{figure}[t]
\begin{center}
\includegraphics[width=3.2in]{church-relative-space.ps}
\includegraphics[width=3.2in]{church-relative-speed.ps}
\includegraphics[width=3.2in]{church-relative-time.ps}
\vspace{-1.5em}
\end{center}
\caption{Relative improvements over the baseline analyzer for the
  \Church{} benchmark in terms of peak memory usage, the rate of state
  transitions, and total analysis time. (Bigger is better.) Each point
  is marked with the section that introduces the optimization.}
\label{fig:churchtime}
\end{figure}

@@

There are a few steps to consider:
\begin{itemize}
 \item{Define special value lattice elements for compound data domains that can be quoted
       (e.g. {\tt QPair} for $\left\{ ({\tt cons} a_i d_i)\right\}_i$, {\tt QVector} for immutable vectors, etc.)}
 \item{Define a ``larger'' value lattice element for all quotable data, {\tt QData}}
 \item{Interpret {\tt (quote (a ...))} as {\tt (qlist a ...)}, a new primitive function defined in figure \ref{fig:qlist},
       and similar definitions for immutable vectors.}
 \item{Extend the $\interpdelta$ axioms to include conservative
   meaning for these new values (e.g. {\tt (car QData)} = {\tt QData},
   {\tt (add1 QData)} = {\tt Number} and log ``possible type error'')
   and allow them to allocate addresses and change the store}
\end{itemize}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=3.2in]{church-relative-space.ps}
\includegraphics[width=3.2in]{church-relative-speed.ps}
\includegraphics[width=3.2in]{church-relative-time.ps}
\vspace{-1.5em}
\end{center}
\caption{Relative improvements over the baseline analyzer for the
  \Church{} benchmark in terms of peak memory usage, the rate of state
  transitions, and total analysis time. Each point is marked with the
  section that introduces the optimization.}
\label{fig:churchtime}
\end{figure}

@@

There are a few steps to consider:
\begin{itemize}
 \item{Define special value lattice elements for compound data domains that can be quoted
       (e.g. {\tt QPair} for $\left\{ ({\tt cons}\ a_i\ d_i)\right\}_i$, {\tt QVector} for immutable vectors, etc.)}
 \item{Define a ``larger'' value lattice element for all quotable data, {\tt QData}}
 \item{Interpret {\tt (quote (a ...))} as {\tt (qlist a ...)}, a new primitive function defined in figure \ref{fig:qlist},
       and similar definitions for immutable vectors.}
 \item{Extend the $\interpdelta$ axioms to include conservative
   meaning for these new values (e.g. {\tt (car QData)} = {\tt QData},
   {\tt (add1 QData)} = {\tt Number} and log ``possible type error'')
   and allow them to allocate addresses and change the store}
\end{itemize}
